Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-24 journal/article.tex
Spellcheck

The definition of large scale was discussed in a workshop at XP2013
\cite{Dingsoyr2013a}. Proceeding the workshop, Dingsøyr et al.
compiled a description of the definition of large scale \cite{Dingsoyr2013b}.
The most common view in the XP2013 workshop was that the involvment of many
people is the main factor in large scale \cite{Dingsoyr2013b}.

Dingsøyr et al. conducted a brief literature search to identify what definitions
on large scale are used \cite{Dingsoyr2013b}. The results showed that large
scale had been regadred in terms of size in persons or teams, project budget,
code base size, and project duration. As examples from the results, Paasivaara
et al. \cite{Paasivaara2008} referred to an organization of 40 people and 7
teams. Berger and Beynon-Davies \cite{Berger2009} present the project cost of
over £10 million as a factor of large scale, but also highlight a team size of
over 50 people. A product with a code base size of over 5 million lines of code
was considered to represent a large scale development effort by Petersen and
Wohlin \cite{Petersen2010}. A project time of 2 years was considered as a factor
of large scale by Bjarnson et al. \cite{Bjarnason2011}, as well as a project
scope of 60-80 features.

As a part of our research, we identified further definitions of large scale. All
of these definitions referred to the number of people involved.
In early work on agile Fowler \cite{Fowler2000} regards the Crystal methodology
being suitable for up to 50 people, thus setting a boundary beyond which agile
methods would be expected to need special considerations. Also Williams and
Cockburn \cite{Williams2003} present 50 people as a limit which practicioners
and researchers has seen as the largest organization suitable for agile.
Elshamy and Elssamadisy \cite{Elshamy2006} considered a development project
large if it had a staff between 50 and 100 people, including all project
personnel. Finally, the largest numbers were presented by Moore and Spens
\cite{Moore2008} who define large scale in the scope of their research as 300
people across 3 sites.

Based on these findings we defined large scale in the scope of this research to
denote organizations with 50 or more people. These 50 people would not all need
to be developers, but they should be part of the development organization. For
instance, Scrum masters and software architects would be counted in. As some
studies presented the number of teams rather than number of people, we
correspondignly defined large scale to denote development efforts involving at
least 6 teams. Having 6 teams with an average teams size of 6 people, plus a
number of supporting staff, can reasonably be considered to form an organization
of 50 people.

@@

The research was conducted as an application of Kitchenham's
\cite{Kitchenham2007} guidelines for systematic literature review. Selection of
primary studies was done using first a keyword based database search to identify
potentially relevant sources, and then manually filtering the search result. The
filtering process was executed independently by two researchers (Dikert,
Paasivaara). The selected primary studies were coded for qualitative data
extraction by one researcher (Dikert). The results of the study were finally
elicitated by aggregating and analyzing the coding of the primary documents.
Figure \ref{fig:researchprocess} presents an outline of the research process.
The entire process was audited and mentored by a third researcher (Lassenius).

@@

The gathering of potential primary studies was based on a search in online
databases. The databases searched are listed in Table \ref{table:databases}. All
databases supported use of complex Boolean logic in searches, which allowed us
flexibility in constructing the search strings. The main task in the database
search was to construct a search string which yielded a reasonably large result
set. The set of matched primary studies was later ammended with a small number
of studies found in references of the matched papers.

@@

In parallell with the full text filtering step the references of all papers were
also examined for relevance. Most papers used references very scarcely, typicaly
referencing well known descriptions of agile methods. We included 2 referenced
papers in full text analysis.

@@

The second part of the research that may have been affected by subjective bias
was the elicitation of results by coding and analysis. Our tools for mitigating
this threat were limited, as the work stages in question are particularly
laborous. For resource constraints the process could not be duplicated. We
assessed the bias of the coding step using an experiment, and prevented
subjective bias in analysis by making the results as tracable as possible. The
coding experiment revealed that two researchers can find roughly 2 of 3 themes
in an experience report identically. Traceability of results was achieved by
supplying references to each claim presented in the results.

@@

A particular problem in this systematic literature review was the limitations of
boolean keyword searches in online databases. A keyword search can not identify
the facet of \emph{large scale}, and also \emph{transformation} is difficult to
capture with keywords. Because of this we assume that it is likely that a some
studies have been missed by the keyword search, potentially causing bias. To
eliminate the potential bias we would suggest manually searching the entire
archive of \emph{Agile Conference} and \emph{Agile Processes in Software
Engineering and Extreme Programming} for relevant studies. These two conferences
provided more than two thirds of the primary sources.

>>>>

The definition of large scale was discussed in a workshop at XP2013
\cite{Dingsoyr2013a}. Proceeding the workshop, Dingsøyr et al.
compiled a description of the definition of large scale \cite{Dingsoyr2013b}.
The most common view in the XP2013 workshop was that the involvement of many
people is the main factor in large scale \cite{Dingsoyr2013b}.

Dingsøyr et al. conducted a brief literature search to identify what definitions
on large scale are used \cite{Dingsoyr2013b}. The results showed that large
scale had been regarded in terms of size in persons or teams, project budget,
code base size, and project duration. As examples from the results, Paasivaara
et al. \cite{Paasivaara2008} referred to an organization of 40 people and 7
teams. Berger and Beynon-Davies \cite{Berger2009} present the project cost of
over £10 million as a factor of large scale, but also highlight a team size of
over 50 people. A product with a code base size of over 5 million lines of code
was considered to represent a large scale development effort by Petersen and
Wohlin \cite{Petersen2010}. A project time of 2 years was considered as a factor
of large scale by Bjarnson et al. \cite{Bjarnason2011}, as well as a project
scope of 60-80 features.

As a part of our research, we identified further definitions of large scale. All
of these definitions referred to the number of people involved.
In early work on agile Fowler \cite{Fowler2000} regards the Crystal methodology
being suitable for up to 50 people, thus setting a boundary beyond which agile
methods would be expected to need special considerations. Also Williams and
Cockburn \cite{Williams2003} present 50 people as a limit which practitioners
and researchers has seen as the largest organization suitable for agile.
Elshamy and Elssamadisy \cite{Elshamy2006} considered a development project
large if it had a staff between 50 and 100 people, including all project
personnel. Finally, the largest numbers were presented by Moore and Spens
\cite{Moore2008} who define large scale in the scope of their research as 300
people across 3 sites.

Based on these findings we defined large scale in the scope of this research to
denote organizations with 50 or more people. These 50 people would not all need
to be developers, but they should be part of the development organization. For
instance, Scrum masters and software architects would be counted in. As some
studies presented the number of teams rather than number of people, we
correspondingly defined large scale to denote development efforts involving at
least 6 teams. Having 6 teams with an average teams size of 6 people, plus a
number of supporting staff, can reasonably be considered to form an organization
of 50 people.

@@

The research was conducted as an application of Kitchenham's
\cite{Kitchenham2007} guidelines for systematic literature review. Selection of
primary studies was done using first a keyword based database search to identify
potentially relevant sources, and then manually filtering the search result. The
filtering process was executed independently by two researchers (Dikert,
Paasivaara). The selected primary studies were coded for qualitative data
extraction by one researcher (Dikert). The results of the study were finally
elicited by aggregating and analyzing the coding of the primary documents.
Figure \ref{fig:researchprocess} presents an outline of the research process.
The entire process was audited and mentored by a third researcher (Lassenius).

@@

The gathering of potential primary studies was based on a search in online
databases. The databases searched are listed in Table \ref{table:databases}. All
databases supported use of complex Boolean logic in searches, which allowed us
flexibility in constructing the search strings. The main task in the database
search was to construct a search string which yielded a reasonably large result
set. The set of matched primary studies was later amended with a small number
of studies found in references of the matched papers.

@@

In parallel with the full text filtering step the references of all papers were
also examined for relevance. Most papers used references very scarcely, typically
referencing well known descriptions of agile methods. We included 2 referenced
papers in full text analysis.

@@

The second part of the research that may have been affected by subjective bias
was the elicitation of results by coding and analysis. Our tools for mitigating
this threat were limited, as the work stages in question are particularly
laborious. For resource constraints the process could not be duplicated. We
assessed the bias of the coding step using an experiment, and prevented
subjective bias in analysis by making the results as traceable as possible. The
coding experiment revealed that two researchers can find roughly 2 of 3 themes
in an experience report identically. Traceability of results was achieved by
supplying references to each claim presented in the results.

@@

A particular problem in this systematic literature review was the limitations of
Boolean keyword searches in online databases. A keyword search can not identify
the facet of \emph{large scale}, and also \emph{transformation} is difficult to
capture with keywords. Because of this we assume that it is likely that a some
studies have been missed by the keyword search, potentially causing bias. To
eliminate the potential bias we would suggest manually searching the entire
archive of \emph{Agile Conference} and \emph{Agile Processes in Software
Engineering and Extreme Programming} for relevant studies. These two conferences
provided more than two thirds of the primary sources.
